---
title: "Notes: MS 204 Chapter 1 part III"
output: pdf_document
fontsize: 11pt 
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
```

### Overview

- Categorical Data & visualizations
- Bivariate visualizations & linear regression


## Categorical data

Ex: $X$ = carrier, $Y$ = origin

```{r, message = FALSE, warning = FALSE}
library(tidyverse); library(oilabs); library(mosaic)
data(nycflights)
nycflights %>% select(carrier, origin) %>% head(3)
```

```{r}
tally(~ origin, data = nycflights)
tally(origin ~ carrier, data = nycflights, margins = TRUE)
```

1. P(X = "AA")
2. P(Y = "LGA")
3. P(Y = "LGA" | X = "AA")
4. P(X = "AA" | Y = "LGA")
5. P(X = "AA", Y = "LGA")

### Visualizing categorical data

```{r, message = FALSE, warning = FALSE, fig.height=2.5, fig.width=5.3}
qplot(x = carrier, data = nycflights)
```


```{r, message = FALSE, warning = FALSE, fig.height=2.9, fig.width=5.3}
ggplot(aes(x = carrier, fill = origin), data = nycflights) + 
  geom_bar()
```

**Aside** What other visualizations would have been possible with this data set?


\newpage

## Bivariate relationships

```{r, message = FALSE, warning = FALSE, fig.height=2.9, fig.width=5.3}
SAT %>% head()
qplot(x = salary, y = expend, data = SAT)
```

### Correlation

\vspace{80pt}

**Aside**: Identify pairs of variables with a correlation coefficient of -0.9, -0.5, 0, 0.5 and 0.9


\newpage 


### Fitting a line

\vspace{80pt}

```{r, message = FALSE, warning = FALSE, fig.height=2.9, fig.width=5.3}
SAT %>% head()
SAT %>% summarize(cor.sat = cor(salary, expend), 
                  mean.salary = mean(salary), 
                  sd.salary = sd(salary), 
                  mean.expend = mean(expend), 
                  sd.expend = sd(expend))
```

\vspace{80pt}


- Interpretations

