---
title: "Notes: MS 204 Chapter 1 part I"
output: pdf_document
fontsize: 12pt 
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
```

### Overview

- Data basics
- Data collection principles
- Sampling and experiments

### Data basics


```{r, message = FALSE, warning = FALSE}
library(tidyverse)
library(gapminder)
gapminder %>% head(4)
```

- Elements of a data frame

\vspace{40pt}

- Variable types

\vspace{40pt}
  
**Aside** Using examples not yet discussed, identify one of each of the four types of variables above

\vspace{40pt}

\newpage 


### Data collection principles

- Anecdotal evidence

- Census

- Observational Studies

- Experiments

\vspace{20pt}

**Aside** Make a table with +'s and -'s to each of the above


\vspace{80pt}


Sampling bias types: 

- Non-response

- Voluntary response

- Convenience sample

- Survivorship bias
    
\vspace{20pt}
  
Examples: Alf Landon versus FDR
  
\vspace{40pt}

Why sample? Exploratory analysis to inference


\vspace{20pt}

Obtaining good samples

- Simple random sample 

- Stratified sample

- Cluster sample
  


\vspace{20pt}

Obtaining good experiments

- Placebo effect and placebo treatments
  
- Blocking
  

