---
title: "Notes: MS 204 Chapter 1/5"
output: pdf_document
fontsize: 11pt 
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE, fig.height =2.5, fig.width = 4.5)
```

### Overview

- Multivariate thinking

## Simple linear regression

Ex: $X$ = salary, $Y$ = SAT

```{r, message = FALSE, warning = FALSE}
library(tidyverse); library(mosaic)
SAT %>% summarise(cor.SAT = cor(sat, salary))
qplot(x = salary, y = sat, data = SAT) + 
  geom_smooth(method = "lm")
fit <- lm(sat ~ salary, data = SAT)
msummary(fit)
```

\newpage


- Describe the association between salary and sat on a state-level basis


\vspace{40pt}


- Identify possible explanations for this finding 

\vspace{60pt}



- Write the estimated regression line


\vspace{40pt}


- Interpret the itercept and the slope in the context of this example


\vspace{80pt}



- Find the residual for Alabama, a state that pays teachers 31.1 thousand dollars per year and boasts an average SAT of 1029.



\vspace{60pt}


### Confounding variables

\newpage



## Thinking multivariately


Ex: $X$ = salary, $Y$ = SAT

```{r, message = FALSE, warning = FALSE}
library(tidyverse); library(mosaic)
SAT <- SAT %>% mutate(frac.cat = cut_number(frac, 3))
SAT %>% tail(5)                      
SAT %>% 
  group_by(frac.cat) %>% 
  summarise(cor.SAT = cor(sat, salary))
qplot(x = salary, y = sat, colour = frac.cat, lty = frac.cat, data = SAT) + 
  geom_smooth(method = "lm")
```


- Describe the association between salary and sat on a state-level basis when taking into account the fration of each state that took the SAT


\vspace{40pt}


- Possible explanations
