---
title: "Notes: MS 204 Chapter 2 part II"
output: pdf_document
fontsize: 11pt 
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE, fig.width = 5, fig.height = 4)
```

### Overview

- Hypothesis testing framework -- single proportion
- Simulating an experiment -- single proportion

### Motivating example

**Lucky or good? Patriots winning coin tosses at nearly impossible rate**

    The New England Patriots' continued struggles against tired "gate" 
    suffixes reached a new nadir earlier this week when a statistical 
    quirk regarding the team's pregame coin toss win rate became an actual 
    topic of conversation. The Patriots have won 19 of their last 25 pregame 
    coin flips, which is pretty remarkable considering the whole 50:50 odds thing.
    


```{r, message = FALSE, warning = FALSE}
library(tidyverse)
library(mosaic)
tosses <- c(rep(0, 6), rep(1, 19))
tally( ~ tosses)
```

General question: How likely is it for data as extreme as what is in the sample to occur under the null?

Ex: How likely is it for the Patriots to win 19 or more coin tosses in 25 attempts if the coin toss was really a 50-50 proposition?

### Setting the stage

- Study type, variable types, sample/population

\vspace{50pt}


### Possible claims



\vspace{150pt}



### Simulation


\vspace{120pt}



### Additional hypothesis test notes


\newpage



```{r, message = FALSE, warning = FALSE}
set.seed(0)
tosses <- c(rep(0, 6), rep(1, 19))
tally( ~ tosses)

mean( ~ tosses)
obs <- mean( ~ tosses)
obs

rflip(5, prob = 0.5)

do(1)*rflip(25, prob = 0.5)

NFL.null <- do(1000)*rflip(25, prob = 0.5)

NFL.null %>% head()

qplot(x = prop, data = NFL.null) + 
  geom_vline(aes(xintercept = obs), colour = "red") + 
  ggtitle("Proportion of won coin tosses in 25 attempts")
  

NFL.null %>% summarise(p.value = mean(prop >= obs))
NFL.null %>% summarise(p.value = mean(prop >= obs)*2)
```

### Summary

