---
title: "Notes: MS 204 Chapter 2 - confidence intervals"
output: pdf_document
fontsize: 11pt 
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE, fig.width = 4.3, fig.height = 3)
```

### Overview

- Normal distribution review
- Applying normal model

#### 68-96-99.7 rule (previous notes)

## Applying normal model

**Central Limit Theorem**: 

\vspace{100pt}

**Standard error**: 

\vspace{80pt}

**Z-score in a hypothesis test**: 

\vspace{80pt}

\newpage

#### Ex: Patriots (se = 0.10)

\vspace{200pt}


#### Ex: Yawning (se = 0.13)

\newpage

## Confidence intervals

#### Analogy



\vspace{200pt}


1. What is best guess?

2. More confidence -- wider or narrower?

3. How probable is it that best guess is right?



#### Ex: Patriots (se = 0.10)

\vspace{100pt}


#### Ex: Yawning (se = 0.13)


\vspace{100pt}

\newpage

### Meaning of confidence

```{r, fig.height= 5, fig.width=6}
library(mosaic)
set.seed(5)
NFL.null <- do(50)*rflip(25, prob = 0.5)
NFL.null <- NFL.null %>% 
  mutate(upp = prop + 1.96*0.1, low = prop - 1.96*0.1, 
         contains.null = upp > 0.5 & low < 0.5, 
         id = 1:n())
qplot(id, prop, data = NFL.null) + 
  geom_errorbar(aes(ymin = low, ymax = upp, colour = contains.null, 
                    lty = contains.null)) + 
coord_flip() + 
  labs(title = "50 simulated CIs, n = 25, p = 0.5", 
       x = "Index", y = "Proportion") + 
  geom_hline(aes(yintercept = 0.5))
```


### Changing the confidence level


\vspace{180pt}

### Incorrect language


\vspace{180pt}


### Example 

Implanting a stent in the brain of a patient at risk for a stroke increased the risk of a stroke. The study estimate a 9% increase in the number of patients who had a stroke, and the standard error of this estimate was about 2.8%.Calculate 90, 95, and 99% confidence intervals for the effect of the stent
	

