---
title: "HW 1"
author: "Mike Lopez"
date: "September 2017"
output:
  html_document
---

```{r global_options, include=FALSE, message=FALSE, warning = FALSE}
knitr::opts_chunk$set(eval = FALSE)
library(dplyr)
library(ggplot2)
```

***General instructions for homeworks***: 

+  Make a new R Markdown file (.Rmd) referring to thea assignment on the course Github page
+  Change the heading to include your author name
+  Save the R Markdown file (named as:  [MikeID]-[Homework01].Rmd -- e.g. "mlopez-Lab01.Rmd") to somewhere where you'll be able to access it later (zip drive, My Documents, Dropbox, etc)
+  Your file should contain the code/commands to answer each question in its own code block, which will also produce plots that will be automatically embedded in the output file
+  **Each answer must be supported by written statements (unless otherwise specified) as well as any code used**: In other words, if the answer is `24`, you should write "The answer is 24" (as opposed to just showing the code and output).
+  Include the names of anyone you collaborated with at the top of the assignment

### Part I: 

Open Intro 1.1, 1.4, 1.6, 1.10, 1.14,1.15, 1.17, 1.26, 1.27 (Note: these are located in section 1.8 at the end of the chapter)

#### 1.1:   	

a. 10/43 in the treatment group (23%) versus 2/46 in the control (4%) 

b. This represents a 19% difference, which seems meaningful. At first glance, the treatment seems more effective than the control

c. Answers can vary, but should make sense. Ex: This is a relatively large difference, and I believe the difference to be significant. Ex: With a relatively small number of subjects, this difference could just be due to chance.


#### 1.4

a. The cases are the 706 adults living near NYC (504 white, 202 black). Age (discrete, continuous), sex (categorical, regular/nominal), and ethnicity (categorical, regular/nominal) were measured, as were weight and height (both continuous). Body fat percentage was the outcome (continuous). The research question is how BMI correlates to body fat percentage, and whether or not that differs within genders and ethnicities.

b. The cases were the 129 undergrads. Categorical variables included class, education, and job respect. The number of candies taken was the outcome variable (continuous, discrete). The research question is whether or not individuals who associate themselves with higher social classes are unethical, as judged by taking of candy that was meant for children.  


#### 1.10

a. Explanatory: percent with bachelor’s, per capita income
b. There is a positive link – roughly linear in shape – with a bit more variability in income among those with higher bachelor degree percents. There do not appear ato be any unusual observations
c. No: observational data


### Part II: 

Lab 1: intro to R questions 4 - 7

4.  What years are included in this data set? What are the dimensions of the 
    data frame? What are the variable (column) names?

```{r load-present-data}
library(oilabs)
data(present)
dim(present)
glimpse(present)
tail(present)
```

The `present` data set includes 1940-2013 births, and has 74 rows/3 columns. The variables are `year`, `boys`, and `girls`


5.  How do these counts compare to Arbuthnot's? Are they of a similar magnitude?

These are much larger counts than Arbuthnots, but of similar ratio. 

6.  Make a plot that displays the proportion of boys born over time. What do you see? 
    Does Arbuthnot's observation about boys being born in greater proportion than girls 
    hold up in the U.S.? Include the plot in your response. *Hint:* You should be
    able to reuse your code from Ex 3 above, just replace the dataframe name.

```{r}
present <- present %>% mutate(boy.rate = (boys)/(boys + girls))
qplot(year, boy.rate, data = present)
```

Ratio of boys is greater than 0.5, but is slowly descreasing with time. A slight spike in boys in 1970

7.  In what year did we see the most total number of births in the U.S.? 
    
```{r}
present %>% mutate(total = boys + girls) %>% arrange(-total) %>% head()
```

2007 had the most births
