---
title: "HW 6"
author: "Mike Lopez"
date: "September 2017"
output:
  html_document
---

```{r global_options, include=FALSE, message=FALSE, warning = FALSE}
knitr::opts_chunk$set(eval = TRUE, message = FALSE, warning = FALSE)
library(dplyr)
library(ggplot2)
```

***General instructions for homeworks***: 

+  Make a new R Markdown file (.Rmd) referring to thea assignment on the course Github page
+  Change the heading to include your author name
+  Save the R Markdown file (named as:  [MikeID]-[Homework01].Rmd -- e.g. "mlopez-Lab01.Rmd") to somewhere where you'll be able to access it later (zip drive, My Documents, Dropbox, etc)
+  Your file should contain the code/commands to answer each question in its own code block, which will also produce plots that will be automatically embedded in the output file
+  **Each answer must be supported by written statements (unless otherwise specified) as well as any code used**: In other words, if the answer is `24`, you should write "The answer is 24" (as opposed to just showing the code and output).
+  Include the names of anyone you collaborated with at the top of the assignment

### Part I: 

Chapter 3 questions: 3.5, 3.6, 3.8, 3.9, 3.12 


### Part II

Return to the `okcupiddata` package. 

```{r}
library(okcupiddata)
library(tidyverse)
```

It is reported that among online dating sites, 60 percent of users are men. Our goal is to compare the sample profiles of OKCupid users to this threshold.

1. State a null and alternative hypothesis.

2. Test the claim that 60 percent of online dating site users are men using simulation based methods designed in Chapter 2.

3. Test the claim that 60 percent of online dating site users are men using normal distribution assumptions from Chapter 3. Are conditions met to use the Normal distribution?

4. Compare your results from the two questions above.

