---
title: "HW 6"
author: "Mike Lopez"
date: "September 2017"
output:
  html_document
---

```{r global_options, include=FALSE, message=FALSE, warning = FALSE}
knitr::opts_chunk$set(eval = TRUE, message = FALSE, warning = FALSE)
library(dplyr)
library(ggplot2)
```

### Part I: 

Chapter 3 questions: 3.5, 3.6, 3.8, 3.9, 3.12  


3.8

a. Z-score * SE = 1.96 * sqrt(.66*(1-0.66))/1018 = 0.03

b. No: The confidence interval for the true proportion of adults who believe licensed drivers should be required to retake their road test is (0.63,0.69), which is not greater than 70%.

3.12 	

a. sample statistic; comes from the data
b. Lower bound: 0.48-1.96 * sqrt(.48*(1-0.48)/1259 ) = 0.452
	
Upper bound: 0.48+1.96 * sqrt(.48*(1-0.48)/1259 ) = 0.508

We are 95% confidence the true proportion of Americans who think marijuana should be legal is between 45.2% and 50.8%.

c. Yes: there is a large enough sample size here (10 successes, 10 failures), and we can assume independence from this survey type

d. While it’s possible the majority of Americans believe this statement, it’s also possible that the majority of Americans do not believe this statement because the confidence interval contains 50%. This statement is not justified




## Part II: Gender discrimination in the workplace? 

Return to the `okcupiddata` package. 

```{r}
library(okcupiddata)
library(tidyverse)
```

It is reported that among online dating sites, 60 percent of users are men. Our goal is to compare the sample profiles of OKCupid users to this threshold.

1. State a null and alternative hypothesis.

2. Test the claim that 60 percent of online dating site users are men using simulation based methods designed in Chapter 2.

3. Test the claim that 60 percent of online dating site users are men using normal distribution assumptions from Chapter 3. Are conditions met to use the Normal distribution?

4. Compare your results from the two questions above.


```{r}
library(okcupiddata)
library(tidyverse)
library(mosaic)
prop.test(~ sex, data = profiles, p = 0.6, success = "m")
null <- do(1000)*rflip(59946, prob = 0.6)
qplot(null$prop)
mean(null$prop <= 0.5976879)
```

