---
title: "HW 7"
author: "Mike Lopez"
date: "September 2017"
output:
  html_document
---

```{r global_options, include=FALSE, message=FALSE, warning = FALSE}
knitr::opts_chunk$set(eval = TRUE, message = FALSE, warning = FALSE)
library(dplyr)
library(ggplot2)
```

***General instructions for homeworks***: 

+  Make a new R Markdown file (.Rmd) referring to thea assignment on the course Github page
+  Change the heading to include your author name
+  Save the R Markdown file (named as:  [MikeID]-[Homework01].Rmd -- e.g. "mlopez-Lab01.Rmd") to somewhere where you'll be able to access it later (zip drive, My Documents, Dropbox, etc)
+  Your file should contain the code/commands to answer each question in its own code block, which will also produce plots that will be automatically embedded in the output file
+  **Each answer must be supported by written statements (unless otherwise specified) as well as any code used**: In other words, if the answer is `24`, you should write "The answer is 24" (as opposed to just showing the code and output).
+  Include the names of anyone you collaborated with at the top of the assignment

### Part I: 

Chapter 4 questions: 4.1, 4.5, 4.8, 4.9, 4.14



### Part II

Return to Lab 6

The question of atheism was asked by WIN-Gallup International in a similar 
survey that was conducted in 2005. (We assume here that sample sizes have 
remained the same.) Table 4 on page 13 of the report summarizes survey results 
from 2005 and 2012 for 39 countries.

For some of the exercises below we will conduct inference comparing two proportions. In
such cases we have a response variable that is categorical, and an exaplanatory variable
that is also categorical, and we are comparing the proportions of success of the response
variable across the levels of the explanatory variable. This means, in the `inference` function
we need to specify both variables, response as `y` and explanatory as `x`.

```{r eval=FALSE}
inference(y = name_of_response_variable, x = name_of_explanatory_variable, ...)
```


1.   Is there convincing evidence that Spain has seen a change in its atheism index 
    between 2005 and 2012? Write out the hypotheses for any tests you 
    conduct and outline the status of the conditions for inference. If you find a 
    significant difference, also quantify this difference with a confidence interval. \
    *Hint:* First create a new data set for respondents from Spain. Also, modify the
    code for the inference function changing the type to run a hypothesis test and
    adding arguments for the null value and the alternative hypothesis. See the help
    for the `inference` function using `?inference` to determine the appropriate syntax.

2.   Is there convincing evidence that the US has seen a change in its atheism index 
    between 2005 and 2012? As always, write out the hypotheses for any tests you 
    conduct and outline the status of the conditions for inference. If you find a 
    significant difference, also quantify this difference with a confidence interval.

3.   If in fact there has been no change in the atheism index in the countries 
    listed in Table 4, in how many of those countries would you expect to 
    detect a change (at a significance level of 0.05) simply by chance?\
    *Hint:* Review the definition of the Type 1 error.

4.   Suppose you're hired by the local government to estimate the proportion of 
    residents that attend a religious service on a weekly basis. According to 
    the guidelines, the estimate must have a margin of error no greater than 
    1% with 95% confidence. You have no idea what to expect for $p$. How many 
    people would you have to sample to ensure that you are within the 
    guidelines?\
    *Hint:* Refer to an earlier plot of the relationship between $p$ and margin of 
    error. This question does not require using the dataset.
