---
title: "HW 8 solutions"
author: "Mike Lopez"
date: "September 2017"
output:
  html_document
---

```{r global_options, include=FALSE, message=FALSE, warning = FALSE}
knitr::opts_chunk$set(eval = TRUE, message = FALSE, warning = FALSE)
library(dplyr)
library(ggplot2)
```

### Part I

**4.30: We’ll use a two-sample t-test for the difference in the mean MPG between automatic and manual cars. 
The point estimate is 19.85-16.12 = 3.73. The standard error is sqrt(3.582/26+4.512/26) = 1.13. 
The test statistic is t = (3.73 – 0)/ 1.13 = 3.3, with a p-value of `2*(1-pt(3.3, df = 25)) = 0.003`. The degrees of freedom is 25. Given this result, there is strong evidence that there’s a difference in the MPG between automatic and manual cars.**


### Part II

Return to Lab 7 and the `nc` data set

1.  Calculate a 95% confidence interval for the average length of pregnancies 
(`weeks`) and interpret it in context. Confirm this answer by hand (use the sample mean, sample standard deviation, and sample size, along with a critical t value). 

```{r}
library(tidyverse)
library(oilabs)
data(nc)
inference(y = weeks, data = nc, type = "ci", method = "theoretical", statistic = "mean")
nc %>% summarise(ave.weeks = mean(weeks, na.rm = TRUE), sd.weeks = sd(weeks, na.rm = TRUE))
qt(df = 999, .025)
38.33 - 1.96*2.9315/sqrt(1000)
38.33 + 1.96*2.9315/sqrt(1000)
```


**We are 95 percent confidence that the true length of pregnancy lies between 38.14 and 38.52 weeks. Our answers using R and by hand are identical**



4.  Now, a non-inference task: Determine the age cutoff for younger and mature 
mothers. Use a method of your choice, and explain how your method works. It is not sufficient to look this answer up in the data. 

**The age cutoff is 35 years or above for mature mothers -- you can use several different code types for this. As an example:**

```{r}
nc %>% group_by(mature) %>% summarise(age.min = min(mage, na.rm = TRUE), age.max = max(mage, na.rm = TRUE))
```


