---
title: "Introduction to multivariate thinking"
output:
  html_document
---

```{r global-options, include=FALSE}
knitr::opts_chunk$set(eval = FALSE)
library(dplyr)
library(ggplot2)
```

## Getting started

### Load packages

In this lab we will explore the data using the dplyr package and visualize it 
using the ggplot2 package for data visualization. Our chosen data set is the `gapminder` data set, nicely set up in
R via Jenny Bryan's `gapminder` package.

Let's load the packages

```{r load-packages, message=FALSE}
library(dplyr)
library(ggplot2)
## install.packages(gapminder)
library(gapminder)
head(gapminder)
```

Our primary interest in this data set is to identify how life expectency has changed over time, and whether or not those changes have been consistency in each continent.

### The data

The gapminder data set contains six variables, each of which vary over time. As a warm-up and to refresh where we left off last time, answer the following questions.

1. Use R code to identify the span of years (e.g., 1920 - 2006), the number of countries, and number of continents included in the gapminder data set.

2. Use the `filter` command to find the gdp per capita of Norway in 1977. 

3. Which continent boasted countries with the largest average life expectency in the year 2007?

### Going further

Let's start by identifying changes over time. One easy thing to do would be to look at a scatter plot

```{r}
qplot(year, lifeExp, data = gapminder)
```

Unfortunately, that scatter plot doesn't do a great job of accounting for overlap. There could be several points and all we'd see is one dot!

There are a few ways to acocunt for this. One is to use the jitter command. Another is to use a different shading for each point -- instead of a complete black point, we can make each point transparent. 

Try the following code.

```{r}
qplot(x = as.factor(year), y = lifeExp, data = gapminder, geom = "boxplot" ) +
  geom_jitter(position = position_jitter(width = 0.1, height = 0), alpha = 1/4)
```

4. Describe changes to the median life expectency across all countries over time.

5. Describe changes to the shape of life expectency across all countries over time.

6. Identify the point (or pair of points) that seem most outlandish. Use the `filter()` command to identify those countries. Any guesses? 

7. Identify what `geom_jitter`, `position_jitter` and `alpha` do to the countries. Feel free to use Stack Overflow or the Help tab to get started.


## Grouping and faceting

Instead of considering each country on its own, let's see if there are any differences in the association between year and life expectency by continent.

```{r}
gapminder1 <- gapminder %>% filter(continent != "Oceania")
qplot(x = year, y = lifeExp, group = country, color = country, data = gapminder1, show.legend = FALSE) +
  geom_line(show.legend = FALSE) + 
  facet_wrap(~ continent) +
  scale_color_manual(values = country_colors) 
```

There is lots to unpack, but the visualization is quite interesting. 

First, let's go step by step through the code. Above, there are steps that

- filter out Oceania, which contains Australia and New Zealand (only two countries)
- uses a different color for each country
- adds a line graph
- hides the legend for both points and lines (otherwise we'd see every country's color!)
- uses a facet to show each continent on its own
- uses a manual scale (`country_colors`), which is specific to this data set.

8. How does accounting for continent change your perception of the increase in life expectency? Identify how the association between year and life expectency varies by continent.

9. The graph also gives insight into differences between countries as far as life expectency. Which continent's show the least and greatest amount of variation?


* * *

## More Practice

1. Make a graph showing the relationship between gdp per capita (x-axis) and life expectency, using all countries. Describe the association

2. Create a new variable, `log.gdpPercap`, which is the log of gdp per capital. As a hint, you can quickly calculate logs using `log()`. Replicate your plot above, using `log.gdpPercap` in place of `gdpPercap`. What is the advantage of taking the log?

3. Facet your graph above (the one using `log.gdpPercap`) so that you see one scatter plot for each year. How has the association between log gdp per capita and life expectency changed over time?


  