---
title: "Notes: MS 204 Chapter 1 part II"
output: pdf_document
fontsize: 11pt 
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
```

### Overview

- Numerical data
- Univariate visualizations for numerical data

  
### Numerical data

Univariate: For random variable $X$, we set out to collect $X_1$, $X_2$, ... $X_n$. The observed data is defined as $X_1 = x_1$, $X_2 = x_2$, ... $X_n = x_n$

Center
    
\vspace{50pt}

Shape
\vspace{50pt}

Spread
\vspace{50pt}

```{r, message = FALSE, warning = FALSE}
library(tidyverse)
library(gapminder)
summary(mtcars$mpg)
```

#### Population versus sample


#### Parameter versus statistic 

\vspace{20pt}

**Aside**: Sketch the expected distributions of (i) number of piercings, (ii) scores on an exam, (iii) IQ scores

\newpage

#### Visualizing numerical data

```{r, message = FALSE, warning = FALSE, fig.height=2.5, fig.width=3.3}
qplot(x = mpg, data = mtcars, geom = "histogram")
```


```{r, message = FALSE, warning = FALSE, fig.height=2.5, fig.width=3.3}
qplot(x = mpg, data = mtcars, geom = "density")
```


```{r, message = FALSE, warning = FALSE, fig.height=2.5, fig.width=5.3}
qplot(x = continent, y = lifeExp, data = gapminder, geom = "boxplot")
```


**Aside**: Pluses and minuses of each of the above charts

